A Formal Model of Checked C

### 2023-01-13 sandp23/implementation.tex
Adding

\noindent\emph{\_TLIB}:
This qualifier relaxes type-checking rules on library functions avoiding unnecessary copying of tainted data.
Specifically, this annotation enables developers to pass tainted pointers as arguments to library functions in~\cregion.
For instance, consider that in~\cregion, we want to string concat~\code{n} characters from tainted pointer~\code{t_str} to~\code{dst} (a checked pointer).
We cannot use~\code{strncat} because our type-checker restricts this as it expects both the pointers to be non-tainted as we are in~\cregion.
We need to either implement the logic for string concatenation in~\cregion or first copy the contents of~\code{t_str} into a~\cregion temporary buffer (sat~\code{tmp}) and then call~\code{strncpy} as~\code{strncat(dst, tmp, n);}.
Both of these approaches are inefficient and, if not done correctly, might result in security bugs.
If the developer knows that~\code{strncat} accesses only~\code{n} bytes from the source buffer, she would like to directly use~\code{strncat} with tainted source pointer in~\cregion.
The~\code{_TLIB} qualifier enables this as shown below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
// Put your example annotation here.
strncpy(dst, t_str, n);
\end{minted}
\aravind{Fix the above code}
Once annotated, our type-checker allows tainted arguments to~\code{strncat} functions.

>>>>

\noindent\emph{\_TLIB}:
This qualifier relaxes type-checking rules on library functions avoiding unnecessary copying of tainted data.
Specifically, this annotation enables developers to pass tainted pointers as arguments to library functions in~\cregion.

For instance, consider that in~\cregion, we want to string concat~\code{n} characters from tainted pointer~\code{t_str} to~\code{dst} (a checked pointer).
We cannot use~\code{strncat} because our type-checker restricts this as it expects both the pointers to be non-tainted as we are in~\cregion.
We need to either implement the logic for string concatenation in~\cregion or first copy the contents of~\code{t_str} into a~\cregion temporary buffer (sat~\code{tmp}) and then call~\code{strncpy} as~\code{strncat(dst, tmp, n);}.
Both of these approaches are inefficient and, if not done correctly, might result in security bugs.
If the developer knows that~\code{strncat} accesses only~\code{n} bytes from the source buffer, she would like to directly use~\code{strncat} with tainted source pointer in~\cregion.
The~\code{_TLIB} qualifier enables this as shown below:
\begin{minted}[mathescape, escapeinside=||, fontsize=\footnotesize]{c}
// Put your example annotation here.
strncpy(dst, t_str, n);
\end{minted}
\aravind{Fix the above code}
The above qualifier relaxes type-checking for all the arguments to the calls to~\code{strncat}, enabling the developer to use the function freely in~\cregion.
